A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Distinguish between labelled input graphs and our bitstring labels

\section{The \McSplit\ Algorithm}

@@

\paragraph{Vertex labels and loops} If vertices are labelled, replace ${\langle
V(\graphG),V(\graphH) \rangle}$ in \lineref{FirstExpandCall} with a set of label classes,
one for each label that appears on at least one vertex of both $\graphG$ and $\graphH$.
Loops may be treated as a label modifier: assuming the original vertex labels
are positive integers, we replace the label $l$ with $-l$ on each vertex that
has a loop.

>>>>

\section{The \McSplit\ Algorithm \label{sec:mcsplit}}

@@

\paragraph{Vertex labels and loops} If vertices in the input graphs have labels
(as distinct from the bit-string labels described in \cref{sec:mcsplit}),
replace ${\langle V(\graphG),V(\graphH) \rangle}$ in \lineref{FirstExpandCall}
with a set of label classes, one for each label that appears on at least one
vertex of both $\graphG$ and $\graphH$.  If some vertices have loops, we create
two label classes for each input label: one class containing vertices with
loops, and the other containing vertices without loops.
